\section{Introduction}
%\subsection{Background}

%\begin{itemize}

%    \item Introduce the purpose of the report.
%    \item Present the organizational context in which the project/internship took place (company, institution, research unit, research laboratory, etc.).
%    \item Present the problem addressed and the motivation for the work carried out. 
    
%\end{itemize}
This report presents the development and analysis of a capstone project focused on VizML and KG4Vis, two different approaches for visualization recommendation. The project was developed in an academic setting, with the goal of exploring and comparing these two methodologies to recommend data visualizations. 

The main motivation was to analyze and compare these methods and their efficiency in recommending visual encodings.


	
\subsection{Objectives and expected results}
%Indicate the objectives of the work and the expected results.
The primary objectives of this project were to analyze and compare the VizML and KG4Vis approaches for visualization recommendation, to understand the strengths and limitations of each method, particularly in terms of accuracy, explainability, scalability, and computational costs, and to successfully run both models using the provided dataset and evaluate their performance.

The expected results include a detailed comparison of the two approaches, insights into their computational requirements, and a working implementation of both models.	

\subsection{Report structure}

This report is structured as follows:

\begin{itemize}
    \item \textbf{Methodology and Development Process}: Describes the iterative approach, stakeholder roles, and timeline of activities.
    
    \item \textbf{Solution Development}:
    \begin{itemize}
        \item \textit{Approach}: Compares VizML (neural network-based) and KG4Vis (knowledge graph-based) methodologies.
        \item \textit{Technical Implementation}: Details neural network training (VizML) and embedding learning (KG4Vis).
        \item \textit{Visualization Recommendation Process}: Contrasts direct prediction (VizML) and explanation-based recommendations (KG4Vis).
        \item \textit{Pre-Execution Comparative Analysis}: Evaluates technology stacks and core differences.
        \item \textit{Dataset}: Describes the dataset structure and preprocessing steps.
        \item \textit{Training}: Covers feature extraction and model training for both approaches.
        \item \textit{Tests}: Summarizes the challenges with VizML and KG4Vis testing configurations.
        \item \textit{Comparative Analysis}: Discusses performance, scalability, accuracy, and precision metrics.
    \end{itemize}
    
    \item \textbf{Conclusions}: Summarizes the results achieved, lessons learned, and future work.
    
    \item \textbf{Appendix}: Includes meeting logs and command lists for reproducibility.
    
    \item \textbf{References}: List of cited works and resources.
\end{itemize}
%Explain the structure of the report.

